Estimating Real-Time Highstreet Footfall from Wi-Fi Probe Requests

### 2018-12-03 paper/sections/main_study.tex
end of day commits

The locations at which the data were collected are shown in Table
\ref{locations-table}. The locations are chosen for their diverse site
conditions and unique sources of noise around the potential location of the
sensors. The position of the sensor at these locations with respect to the
context is shown the Figure \ref{main_signal_strength}. We can see that Location
5 is the `cleanest' with one clear stationary source of noise (phone shop) of
while location 2 is the one with the most complexity with seating area all
around the sensor.  The sensors were operational through out February and March
while manual counts were conducted in these location in half hour sessions on at
least two different days. For the purposes of comparing with ground truth we
just considered the data from sensors which corresponding to the 12 sets of
available manual counts. The schedule of data collection is shown in Figure
\ref{main_schedule}

>>>>

The locations at which the data were collected are shown in Table
\ref{locations-table}. The locations were chosen for their diverse site
conditions and unique sources of noise around the potential location of the
sensors. The position of the sensor at these locations with respect to the
context is shown the Figure \ref{main_signal_strength}. We can see that Location
5 is the `cleanest' with one clear stationary source of noise (phone shop)
while location 2 is the most complex due to the proximity of seating areas
to the sensor.  The sensors were operational through out February and March,
while manual counts were conducted in these locations in half hour sessions on at
least two different days. For the purposes of comparing with ground truth, we
considered the data from sensors which correspond to the 12 sets of
available manual counts. The schedule of data collection is shown in Figure
\ref{main_schedule}.
